Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-12-04 MDPI_submission.tex
Commit 2023-12-04 12:07

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
Sky conditions & Trend [\%/year] & Trend p-value & Pearson cor. & Days\\
\midrule
All skies & 0.3765 & 0.0000 & 0.0913 & 10251\\
Cloudy skies & 0.3434 & 0.0000 & 0.0729 & 7278\\
Clear skies & 0.0408 & 0.0135 & 0.0348 & 5035\\
\bottomrule
\end{tabu}
\end{table}

>>>>

\caption{\label{tab:trendtable}Trends in SDR daily means for different sky conditions for the period 1993 - 2023.}
\begin{tabu} to \linewidth {>{\centering\arraybackslash}p{8em}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
Sky conditions & Trend [\%/year] & Trend p-value & Pearson cor. & Days\\
\midrule
All skies & 0.3765 & 0.0000 & 0.0913 & 10251\\
Clear skies & 0.0408 & 0.0135 & 0.0348 & 5035\\
Cloudy skies & 0.3434 & 0.0000 & 0.0729 & 7278\\
\bottomrule
\end{tabu}
\end{table}
